%!TEX root = ../csuthesis_main.tex
{~}
\vspace{-9pt}
\section{攻读学位期间主要研究成果} % 无章节编号

\ifblindreview
% \noindent
% （盲审隐去作者相关具体信息）
\fi
\vspace{11pt}
\subsection*{一、学术论文}

\ifblindreview

% 学位办老师要求用如下这种几乎算是单盲的格式，我也木有办法……
\subsubsection*{已录用/检索论文}
%\noindent
第一作者：
\begin{enumerate}[label={[\arabic*]},itemindent=2em,wide]

\item A novel method of gene regulatory network structure inference from gene knock-out expression data[J]. Tsinghua Science and Technology 24, no. 4 (2019): 446-455.{\bfseries \heiti（SCI 检索，JCR 3 区）} 
\item D3GRN: a data driven dynamic network construction method to infer gene regulatory networks[J]. BMC genomics 20, no. 13 (2019): 1-8.{\bfseries \heiti（SCI 检索，JCR 1 区）} 
\item DoRC: Discovery of rare cells from ultra-large scRNA-seq data[C]. In 2019 IEEE International Conference on Bioinformatics and Biomedicine (BIBM), pp. 111-116. IEEE, 2019.{\bfseries \heiti（EI 检索）}

\end{enumerate}
%第二作者：
%\begin{enumerate}[label={[\arabic*]},itemindent=2em,wide]
%\item CSU Latex Template[J]. CSU player: 1(1):1-10. {\bfseries \heiti（SCI 检索，JCR 1 区）}
%\item CSU Latex Template[J]. CSU player: 1(1):1-10. {\bfseries \heiti（SCI 检索，JCR 2 区）}
%\end{enumerate}
%\noindent
\subsubsection*{投稿状态论文}
%\noindent
第一作者：
\begin{enumerate}[label={[\arabic*]},itemindent=2em,wide]
\item scGRNHunter: a gene regulatory network reconstruction method from single cell RNA-seq data[J]. Bioinformatics. {\bfseries \heiti（SCI JCR 1 区）}
\end{enumerate}
%第二作者：
%\begin{enumerate}[label={[\arabic*]},itemindent=2em,wide]
%\item CSU Latex Template. XXX Transactions on CSU player. {\bfseries \heiti（SCI Under Review，JCR 1 区）}
%\item CSU Latex Template. XXX Transactions on CSU player. {\bfseries \heiti（SCI Under Review，JCR 2 区）}
%\end{enumerate}


\else
% 标准版本
\begin{enumerate}[label={[\arabic*]},itemindent=2em,wide]

\item \textbf{Xiang Chen}, Min Li, Ruiqing Zheng, Siyu Zhao, Fang-Xiang Wu, Yaohang Li, and Jianxin Wang. A novel method of gene regulatory network structure inference from gene knock-out expression data. Tsinghua Science and Technology 24, no. 4 (2019): 446-455.{\bfseries \heiti（SCI 检索，JCR 2 区）} 
\item \textbf{Xiang Chen}, Min Li, Ruiqing Zheng, Fang-Xiang Wu, and Jianxin Wang. D3GRN: a data driven dynamic network construction method to infer gene regulatory networks. BMC genomics 20, no. 13 (2019): 1-8.{\bfseries \heiti（SCI 检索，JCR 1 区）} 
\item \textbf{Xiang Chen}, Fang-Xiang Wu, Jin Chen, and Min Li. DoRC: Discovery of rare cells from ultra-large scRNA-seq data. In 2019 IEEE International Conference on Bioinformatics and Biomedicine (BIBM), pp. 111-116. IEEE, 2019.{\bfseries \heiti（EI 检索, CCF B~类推荐国际会议）}
\item \textbf{Xiang Chen}, Min Li, Ruiqing Zheng, Fang-Xiang Wu, and Jianxin Wang. scGRNHunter: a gene regulatory network reconstruction method from single cell RNA-seq data. Bioinformatics. {\bfseries \heiti（拟投稿）}
\item Data-driven clustering recommendation method for single-cell RNA-sequencing data.Yu Tian, Ruiqing Zheng, Zhenlan Liang, {\bf Xiang Chen}, Suning Li, Min Li. IEEE/ACM Transactions on Computational Biology and Bioinformatics.{\bfseries \heiti(投稿中)}
\item Hui Jiang, Mengyun Yang, \textbf{Xiang Chen}, Min Li, Yaohang Li, and Jianxin Wang. miRTMC: A miRNA Target Prediction Method Based on Matrix Completion Algorithm[J]. IEEE JOURNAL OF BIOMEDICAL AND HEALTH INFORMATICS. 2020, DOI:10.1109/JBHI.2020.2987034. {\bfseries \heiti（SCI 检索，JCR 1 区）}
\item Ruiqing Zheng, Zhenlan Liang, \textbf{Xiang Chen}, Yu Tian, Min Li. An Adaptive Sparse Subspace Clustering for Cell Type Identification. Front Genet. 2020 Apr 28;11:407. doi: 10.3389/fgene.2020.00407.{\bfseries \heiti（SCI 检索，JCR 2 区）}
\item Ruiqing Zheng, Min Li, \textbf{Xiang Chen}, Fang-Xiang Wu, Yi Pan, and Jianxin Wang. BiXGBoost: a scalable, flexible boosting-based method for reconstructing gene regulatory networks. Bioinformatics 35, no. 11 (2019): 1893-1900. {\bfseries \heiti（SCI 检索，JCR 1 区）}
\item Ruiqing Zheng, Min Li, \textbf{Xiang Chen}, Siyu Zhao, Fang-Xiang Wu, Yi Pan, Jianxin Wang. An ensemble method to reconstruct gene regulatory networks based on multivariate adaptive regression splines. IEEE/ACM Transactions on Computational Biology and Bioinformatics. DOI: 10.1109/TCBB.2019.2900614  {\bfseries \heiti（SCI 检索，JCR 1 区）}

\item 王荣,王建新,\textbf{陈向},盛羽.面向异构资源集成的数字图像实验平台[J].计算机工程与应用 54, no.15 (2018):185-191.{\bfseries \heiti（EI 期刊）}
\end{enumerate}
\fi

\vspace{22pt}
\subsection*{二、主持和参与的科研项目}
\ifblindreview
\else
\begin{enumerate}[label={[\arabic*]},itemindent=2em,wide]

    \item 国家自然科学基金优秀青年项目:~生物信息学,~项目编号:61622213,参与。

\end{enumerate}

\fi

\newpage

\ifblindreview
\else
% 由于 acknowledgement 比较长，单独使用一个文件来汇总。FIXME:chenxofhit@gmail.com
\input{content/acknowledgement}
\newpage
\fi